SST_patterns

### 2019-11-07 SST_patterns.Rmd
progress

@@

>>>>

```{r}
#glm to determine if there is a difference in the number of events recorded at different at every distance

load("Data/Count/OISST_count.RData")
load("Data/Count/G1SST_count.RData")
load("Data/Count/MUR_count.RData")
load("Data/Count/CMC_count.RData")

options(scipen = 999)
anova_func <- function(df){
  sites_aov <- aov(distance ~ duration * site * site, data = df)
return(sites_aov)
}

SACTN_anov <- aov(intensity_mean ~ site * duration, data = SACTN_upwell_base)
summary(SACTN_anov)

@@

(G1SST_SP_pl <- plot_loli_func(df = G1SST_SEAPOINT))
(G1SST_SB_pl <- plot_loli_func(df = G1SST_SB))
(G1SST_PN_pl <- plot_loli_func(df = G1SST_PN))
(G1SST_LB_pl <- plot_loli_func(df = G1SST_LB))

G1SST_SP_pl <- G1SST_SP_pl +
  ggtitle("D.") #Sea Point
G1SST_SB_pl <- G1SST_SB_pl +
  ggtitle("C.") # Saldanha Bay
G1SST_PN_pl <- G1SST_PN_pl +
  ggtitle("B.")        # Port Nolloth
G1SST_LB_pl <- G1SST_LB_pl +
  ggtitle("A.")#Lamberts Bay

combined_G1SST_pl_2 <- ggarrange(G1SST_SB_pl, G1SST_SP_pl)

combined_G1SST_pl_1 <- ggarrange(G1SST_LB_pl, G1SST_PN_pl)
